---
title: "CodeBook"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Variables

```{r variables}
Xtrain <- read.table("~/work-rfiles/UCI HAR Dataset/train/X_train.txt", header = FALSE)
ytrain <- read.table("~/work-rfiles/UCI HAR Dataset/train/y_train.txt", header = FALSE)
subjecttrain <- read.table("~/work-rfiles/UCI HAR Dataset/train/subject_train.txt", header = FALSE)
Xtest <- read.table("~/work-rfiles/UCI HAR Dataset/test/X_test.txt", header = FALSE)
ytest <- read.table("~/work-rfiles/UCI HAR Dataset/test/y_test.txt", header = FALSE)
subjecttest <- read.table("~/work-rfiles/UCI HAR Dataset/test/subject_test.txt", header = FALSE)
features <- read.table("~/work-rfiles/UCI HAR Dataset/features.txt", header = FALSE)
activitylabels <- read.table("~/work-rfiles/UCI HAR Dataset/activity_labels.txt", header = FALSE)
```
The variables above were used to store the data read from the respective text files. These would include **Xtrain, ytrain, subjecttrain, Xtest, ytest, subjecttest, features**, and **activitylabels**.

```{r variables1}
bindtrain <- cbind(ytrain, subjecttrain, Xtrain)
bindtest <- cbind(ytest, subjecttest, Xtest)
mergeddata <- rbind(bindtrain, bindtest)
```
**bindtrain** and **bindtest** are variables that store the column bind of the variables inside the parenthesis. **mergedata** then stores the row bind of both bindtrain and bindtest.

**getNames** lists down the column names from mergeddata. **meansd** extracts measurements on the mean and standard deviation by creating a vector and only getting the value if it returns TRUE. **descriptivenames** uses descriptive activity names to name the activities in the data set.

Lastly, **secondSet** is a variable that stores the mean of all of the columns for each activity and each subject.

## R Code

The assignment required to implement the following steps and was saved to an R file called **run_analysis.R**:

1. Merges the training and the test sets to create one data set.

2. Extracts only the measurements on the mean and standard deviation for each measurement. 

3. Uses descriptive activity names to name the activities in the data set

4. Appropriately labels the data set with descriptive variable names. 

5. From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

After step 5, the resulting independent tidy data set was saved to a file called **secondSet.txt**.
